Data Exercise

### 2024-06-27 data-exercise/data-exercise.qmd
3rd Time is a charm, I have removed and corrected misspelling of my  .qmd file and rendered it looks fine.

Placeholder file for the future data exercise.
## Running Code
```{r}
library(MASS)
library(synthpop)
library(tidyverse)
library(dplyr)
library(writexl)
library(ggplot2)
library(broom)
```

@@

```{r}
# Linear model plot
ggplot(applicant_final, aes(x = situational, y = performance)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Linear Model: Situational vs Performance", x = "Situational Score", y = "Performance Score")
```
```{r}
# Generalized linear model plot
ggplot(applicant_final, aes(x = situational, y = performance)) +
  geom_point() +
  geom_smooth(method = "glm", se = FALSE, color = "green") +
  labs(title = "Generalized Linear Model: Situational vs Performance", x = "Situational Score", y = "Performance Score")
```

>>>>

Placeholder file for the future data exercise.

## Loading and Checking Data
## Import Libraries
```{r}
library(MASS)
library(synthpop)
library(tidyverse)
library(dplyr)
library(writexl)
library(ggplot2)
library(broom)
```

@@

```{r}
# Linear model plot
ggplot(applicant_final, aes(x = situational, y = performance)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Linear Model: Situational vs Performance", x = "Situational Score", y = "Performance Score")
```

```{r}
# Generalized linear model plot
ggplot(applicant_final, aes(x = situational, y = performance)) +
  geom_point() +
  geom_smooth(method = "glm", se = FALSE, color = "green") +
  labs(title = "Generalized Linear Model: Situational vs Performance", x = "Situational Score", y = "Performance Score")
```
